---
title: "ENM_FBaletaud"
output: html_document
bibliography: stats.modelo1.bib
---
```{r include=FALSE }
knitr::opts_chunk$set(echo = FALSE)
library(rmarkdown)
library(knitr)
library(dismo)
library(raster)
library(rgdal)
library(ncdf4)
library(rgbif)
library(taxize)
library(taxizesoap)
library(devtools)
library(robis)
library(leaflet)
library(tibble)
library(stringr)
library(readr)
library(pryr)
library(marmap)
library(lubridate)
library(broom)
library(mregions)
library(rgeos)
library(ggmap)

```

```{r}
read_chunk("./scripts/00_Environment_variables.R")
read_chunk("./scripts/01_Occurence_data.R")
```


# Getting and formating environmental variables

## Temperature

```{r temperature, eval=FALSE, include=FALSE}

```

## Sea floor geomorphology

```{r seafloor, eval=FALSE, include=FALSE}

```



# Getting and cleaning biodiversity data


Worldwide occurences are downloaded from the [OBIS database](http://www.iobis.org/) using the API through [robis](https://github.com/iobis/robis). The overall method is highly inspired from the OBIS news of Tom Webb [Extracting and Enriching OBIS Data with R](http://www.iobis.org/2016/11/22/sorbycollection/) (2016).

The chunk used here first checks the name using [taxizesoap](https://github.com/ropensci/taxizesoap) which connects to the WoRMS database, a very well known authority in terms of taxonomy.


## OBIS Dataset


The function firstly checks the name of the species we've entered. Then rOBIS aggregates automatically all the occurrences from the accepted name and the ones from the synonym. The collected data is directly filtered using the quality flags [@Vandepitte2015].


```{r OBIS}

```

The occurrences are mapped with the [leaflet package](https://rstudio.github.io/leaflet/), rendering an interactive zoomable map. Different map styles can be used from here (inside the code) ([here](http://leaflet-extras.github.io/leaflet-providers/preview/))

```{r plotocc1}

```

## IUCN dataset

The IUCN data was recovered from the species range on their basemap (eg: [Galeocerdo Cuvier](http://maps.iucnredlist.org/map.html?id=39378)) under the "download Spatial data" link. The data provided is a shapefile. we converted it to a raster of bioclimatic grid resolution and extracted the centroid of each cell to generate "occurrences" from the species range.
Once the data is collected, it is directly extracted inside the ./biodiversity/iucn folder.The folder extracted is named after the same zip file name : "species" collapsed with an IUCN number through an underscore. 
This folder has to be renamed after the studied species with an underscore between Genus and species. (eg: Galeocerdo_cuvier). Inside that folder lie the whole SIG files needed along with the redlists pdf/readme files as metadata



## Manual check

A manual check is proceeded.

One of the Obis quality flag (QC) consists in checking whether the occurence is in the ocean or earth. In order to be sure that no occurrences are defaulting, the ecoregion shape file from WWF is read and matched with occurences intersecting with the shape file to ensure marine only occurrences.

```{r Manualchk}

```



By zooming on the leaflet map, we witness that some points got removed. We can still see a point in the asian region very close to the shore. By zooming in, the satellital map show the occurrence in the middle of an urbanised zone.


The dataset names can be checked to assess where the data is coming from (Since the data already went through the quality flags, the datasets should be more than honorables, unless...)

```{r datasetname}

```


The specimen conserved at the National Taiwan Museum passed the Quality Control flags and the terrestrial control while still being on land.


The number of occurrences now from OBIs is showed below :

```{r NTaiM}

```



## Merging OBIS data with NC data

The global data can now be merged with the regional data collected from the study area (New Caledonia). 

The mapped result

```{r mergeOccs}

```


# References


