---
title: "ENM_FBaletaud"
output: html_document
bibliography: stats.modelo1.bib
---
```{r include=FALSE }
knitr::opts_chunk$set(echo = FALSE)
library(rmarkdown)
library(knitr)
library(dismo)
library(raster)
library(rgdal)
library(ncdf4)
library(rgbif)
library(taxize)
library(taxizesoap)
library(devtools)
library(robis)
library(leaflet)
library(tibble)
library(stringr)
library(readr)
library(pryr)
library(marmap)
library(lubridate)
library(broom)
library(mregions)
library(rgeos)
library(ggmap)

```

```{r}
read_chunk("./scripts/00_Environment_variables.R")
read_chunk("./scripts/01_Occurence_data.R")
```


# Getting and formating environmental variables

## Temperature

```{r temperature, eval=FALSE, include=FALSE}

```

## Sea floor geomorphology

```{r seafloor, eval=FALSE, include=FALSE}

```



# Getting and cleaning biodiversity data



Worldwide occurences are downloaded from the [OBIS database](http://www.iobis.org/) using the API through [robis](https://github.com/iobis/robis). The overall method is highly inspired from the OBIS news from Tom Webb [Extracting and Enriching OBIS Data with R](http://www.iobis.org/2016/11/22/sorbycollection/) (2016)

The chunk used here first checks the name using [taxizesoap](https://github.com/ropensci/taxizesoap) which connects to the WoRMS database, a very well known authority in terms of taxonomy.

OBIS aggregates automatically all the occurrences from the accepted names and the ones from the synonym. The collected data is directly filtered using the quality flags [@Vandepitte2015].



## OBIS Dataset

```{r OBIS}

```



## Manual check

A manual check is proceeded by mapping the occurrences with the [leaflet package](https://rstudio.github.io/leaflet/). Different map styles can be used ([here](http://leaflet-extras.github.io/leaflet-providers/preview/))


The ecoregion shape file from WWF is read and matched with occurences intersecting with the shape file.

```{r Manualchk}

```



By zooming on the leaflet map, we could still witness points on land so they got removed.

The specimen conserved at the National Taiwan Museum passed the Quality Control flags and the terrestrial control so we needed to remove it individualy



## Merging OBIS data with NC data



```{r mergeOccs}

```


# References


